Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-15 Scripts/Initial_Analysis.Rmd
Finally created cilindrical SSR maps!!!!!

# Tranform to tubular
Eez_centroid_sf <-st_as_sf(Eez_centroid,
            coords = c("longitude", "latitude")
            ) %>% 
  st_set_crs(4326) #%>% # to match shapefiles
  # st_transform(crs = "+proj=eck4")

# Transform sf to df
# Eez_centroid_eck <- as.data.frame(Eez_centroid_sf)

# Eez_centroid_eck <- do.call(rbind, st_geometry(Eez_centroid_sf)) %>% 
#   as_tibble() %>% 
#   setNames(c("lon","lat")) %>% 
#   bind_cols(Eez_centroid) %>% 
  # select(eez_name,longitude = lon,latitude = lat)

@@

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  # st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326)
  # sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

time_sets <- c("per_early","per_mid")
i = 1
for(i in 1:2){
  gc()# clean ram

@@

  ggsave(
    plot = Prop_map,
    filename = "./Figures/fig_5n.png",
    width = 10,
    height = 5,
    units = "in"
  )

>>>>

# Tranform to tubular
Eez_centroid_sf <-st_as_sf(Eez_centroid,
            coords = c("longitude", "latitude")
            ) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(crs = "+proj=eck4")

ggplot(Eez_centroid_sf) +
  geom_sf()

# Transform sf to df
Eez_centroid_eck <- as.data.frame(Eez_centroid_sf)

Eez_centroid_eck <- do.call(rbind, st_geometry(Eez_centroid_sf)) %>%
  as_tibble() %>%
  setNames(c("lon","lat")) %>%
  bind_cols(Eez_centroid) %>%
select(eez_name,longitude = lon,latitude = lat)

@@

# Done with the help of https://www.data-to-viz.com/story/MapConnection.html

# A function that makes a dateframe per connection (we will use these connections to plot each lines)
data_for_connection=function( dep_lon, dep_lat, arr_lon, arr_lat, group){
  inter <- gcIntermediate(c(dep_lon, dep_lat), c(arr_lon, arr_lat), n=50, addStartEnd=TRUE, breakAtDateLine=F)             
  inter=data.frame(inter)
  inter$group=NA
  diff_of_lon=abs(dep_lon) + abs(arr_lon)
  if(diff_of_lon > 180){
    inter$group[ which(inter$lon>=0)]=paste(group, "A",sep="")
    inter$group[ which(inter$lon<0)]=paste(group, "B",sep="")
  }else{
    inter$group=group
  }
  return(inter)
}
pal <- wesanderson::wes_palette("Zissou1",100,type = "continuous")

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
  # left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  # left_join(Eez_centroid_eck,
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na()

# Get paths data
path_data <- Data %>% 
  filter(
    variable %in% c("mean_eez")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

data_ready_plot=data.frame()

for(i in c(1:nrow(path_data))){
  tmp=data_for_connection(path_data$start_lon[i], path_data$start_lat[i], path_data$end_lon[i], path_data$end_lat[i] , i)
  # tmp$homecontinent=summary$homecontinent[i]
  tmp$per_early_plot=path_data$per_early_plot[i]
  tmp$per_mid_plot=path_data$per_mid_plot[i]
  tmp$source=path_data$source[i]
  tmp$objective=path_data$target[i]
  data_ready_plot=rbind(data_ready_plot,tmp)
}

data_ready_plot <- data_ready_plot %>% 
  mutate(
    per_early_plot = ifelse(per_early_plot >= 50,50,per_early_plot),
    per_mid_plot = ifelse(per_mid_plot >= 50,50,per_mid_plot))

sf_ready_plot <- st_as_sf(data_ready_plot,
            coords = c("lon", "lat")
            ) %>% 
  st_set_crs(4326) %>% # to match shapefiles
  st_transform(crs = "+proj=eck4")

# Get arrow data
arrows_data <- as.data.frame(st_coordinates(st_cast(sf_ready_plot,"POINT")$geometry)) %>% 
  bind_cols(data_ready_plot)

# Get point data
point_data <- path_data %>% 
  filter(per_early <= 0) %>% 
  st_as_sf(
    coords = c("start_lon", "start_lat")
  ) %>% 
  select(source,target,geometry) %>% 
  st_set_crs(4326) %>% 
  st_transform(crs = "+proj=eck4")

#### Get the change of species

n_trans_eez <- Transboundary_spp %>% 
  group_by(eez_name) %>% 
  summarise(
    # n_trans = unique(length(taxon_key))
    n_trans = n()
  )

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, per_early_plot >= 0), aes(color = per_early_plot), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(arrows_data, per_early_plot >= 0),
              aes(X, Y,
                  group = group,
                  col = per_early_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(data_ready_plot$per_early_plot,na.rm=T)),
                        breaks = seq(0,max(data_ready_plot$per_early_plot,na.rm=T),10),
                        labels = c(seq(0,max(data_ready_plot$per_early_plot-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(data_ready_plot$per_early_plot,na.rm=T)),
                        breaks = seq(0,max(data_ready_plot$per_early_plot,na.rm=T),10),
                        labels = c(seq(0,max(data_ready_plot$per_early_plot-10,na.rm=T),10),">50")
  )

ggsave(plot =  p,
       "./Figures/ssr_early.png",
       width = 10,
       height = 5,
       units = "in")

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
  # left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  # left_join(Eez_centroid_eck,
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  # gather("variable","value",per_early:per_early_plot) %>% 
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  # st_sfc(crs = 4326) %>%
  st_sfc(crs = "+proj=eck4") %>% # for tubular plot
  st_sf(geometry = .) %>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  # st_segmentize(units::set_units(100, km)) %>%
  # mutate(geometry = (geometry + c(18000000,90000000)) %% c(18000000) - c(18000000,90000000)) %>%
  # mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  # st_wrap_dateline(options = "WRAPDATELINE=YES", quiet = TRUE); network_data_sf # for tubular plot
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=60"), quiet = TRUE)

network_data_sf

@@

time_sets <- c("per_early","per_mid")
i = 1
# for(i in 1:2){
  gc()# clean ram

@@

  ggsave(
    plot = Prop_map,
    filename = "./Figures/test.png",
    width = 10,
    height = 5,
    units = "in"
  )
